Palomar 5 Gaps

### 2024-10-21 paper/main.tex
once again made caption better

    We desire to search for some generalizable characterisitcs of the perturbers to see what contrasts them to globular clusters that do not impact the Pal5 Stream. We present a suite of figures to answer for this end in Fig.~\ref{fig:mass_size_plane}. Note that the colors of the markers and histogram bins are

@@

      \includegraphics[width=0.45\linewidth]{impact_geometry_statistics_deltaP.png}
      \includegraphics[width=0.45\linewidth]{impact_stats_phase_space.png}
      \caption{\textbf{Characterisitcs of gap causing clusters}--\textit{Note} that the colors of the markers and histogram bars are consistent with the clusters from \ref{fig:histogram_impact_time}.\\ \textbf{Top Left:} Energy-angular momentum space of the globular clusters in the simulations, with 50~$\times$~165 data points representing all sampled initial conditions. Clusters impacting Palomar 5 are shown with colored markers; non-gap-causing clusters are gray. Palomar 5 is marked with a white symbol and black edge. \\ \textbf{Top Right:} The mass-size plane. Uncertainties on the mass are indicated with vertical bars. \\ \textbf{Bottom Left:} The distribution of imparted momentum from a cluster flyby given by Eq.~\ref{eq:change_in_momentum}. The data set includes the top 5 strongest flybys from each simulation. Those that cause gaps are colored while those that do not are left in black. \\ \textbf{Bottom Right:} Palomar 5's orbit in the meridional plane. The grayscale represents all 50 stacked orbits, with $\mathcal{P}$ indicating the probability of  Palomar~5's position, normalized to $\mathcal{P}_\textrm{max}=1$. Markers show the perturber's position during each impact.}
      \label{fig:mass_size_plane}
      \end{figure*}

>>>>

    We desire to search for some generalizable characterisitcs of the perturbers to see what contrasts them to globular clusters that do not impact the Pal5 Stream. We present a suite of figures to answer for this end in Fig.~\ref{fig:mass_size_plane}.

      \includegraphics[width=0.45\linewidth]{impact_geometry_statistics_deltaP.png}
      \includegraphics[width=0.45\linewidth]{impact_stats_phase_space.png}
      \caption{\textbf{Characterisitcs of gap causing clusters}--\textit{Note} that the colors of the markers and histogram bars are consistent with Fig.~\ref{fig:histogram_impact_time}.\\ \textbf{Top Left:} Energy-angular momentum space of the globular clusters in the simulations, with 50~$\times$~165 data points representing all sampled initial conditions. Clusters impacting Palomar 5 are shown with colored markers; non-gap-causing clusters are gray. Palomar 5 is marked with a white symbol and black edge. The circular velocity-curve is drawn with a light-pink dashed curve.\\ \textbf{Top Right:} The mass-size plane. Uncertainties on the mass are indicated with vertical bars. \\ \textbf{Bottom Left:} The distribution of imparted momentum from a cluster flyby given by Eq.~\ref{eq:change_in_momentum}. The data set includes the top 5 strongest flybys from each simulation. Those that cause gaps are colored while those that do not are left in black. \\ \textbf{Bottom Right:} Palomar 5's orbit in the meridional plane. The grayscale represents all 50 stacked orbits, with $\mathcal{P}$ indicating the probability of  Palomar~5's position, normalized to $\mathcal{P}_\textrm{max}=1$. Markers show the perturber's position during each impact.}
      \label{fig:mass_size_plane}
      \end{figure*}

      From the top left panel of Fig.~\ref{fig:mass_size_plane}, the immediate result is that all clusters that impact Palomar~5's stream are within a band of orbital energies from about $-2\times10^2~\textrm{km/s}^2$ to $-1\times10^2~\textrm{km/s}^2$. This is a non-surprising result indicating that in order for a cluster to perturb Palomar 5's stream, it must enter Palomar~5's orbital space. Additionally, we reproduce the results of \citet{2021MNRAS.505.5978V}, who found a wide range of possible orbital solutions for the least bound clusters, some being retrograde and some prograde. For this potential model, only 3 samplings of a globular cluster had positive energies.

@@
